Live Functional Programming with Typed Holes

### 2018-04-15 calculus.tex
note to Cyrus
nit

We outline the proofs in Appendix~\ref{sec:hole-filling}, along with a
number of other necessary lemmas and definitions.
%
In particular, additional machinery handles the situation wherein a
now-filled non-empty hole had taken a step in the original evaluation.

\matt{We could (should?) move the next paragraph to the appendix, 
before/after the proofs mentioned above; 
its not really adding much to the discussion above, 
but may be interesting to the very studious reader/prover}

>>>>

We outline the proofs in Appendix~\ref{sec:hole-filling}, along with a
number of other necessary lemmas and definitions.
%
In particular, additional machinery handles the situation wherein a
now-filled non-empty hole had taken a step in the original evaluation.
\matt{Cyrus --- I tried to simplify and shorten the earlier version of the prior sentence, but I \emph{may} have unintentionally goofed up what it was trying to say; please double check the prior sentence}

\matt{We could (should?) move the next paragraph to the appendix, 
before/after the proofs mentioned above; 
its not really adding much to the discussion above, 
but may be interesting to the very studious reader/prover; also, leaving it here also gives a cranky reviewer a nice weapon to hit us with}
